Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2024-02-15 src/tex/ms.tex
[showyourwork] overleaf sync

    ]
    \begin{table}
    \centering
        \begin{tabular}{ c|c|c|c|c } 
            \input{output/metrics-table.tex}
        \end{tabular}
        \label{tab:metrics}
        \script{metrics-table.py}
        \caption{Image metrics for the difference source scenarios and methods.}
    \end{table}

@@

    We compute the full-width at half-max (FWHM), $\omega$, of the profiles for each bootstrapped data set, by fitting a Gaussian shape with a linear gradient as a baseline for both the original counts and the \jolideconospace-deconvolved intensities. In both cases we compute the mean of $\omega$. We find that the deconvolved profile is significantly narrower. For the counts profile, $\omega_C=0.78 \pm 0.02$~arcsec, where the error bar is obtained by computing the standard deviations of $\ometa$ over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.58 \pm 0.02$~arcsec.

>>>>

    ]
    \begin{table}
    \centering
        \begin{tabular}{ c|c|c|c|c|c } 
            \input{output/metrics-table.tex}
        \end{tabular}
        \label{tab:metrics}
        \script{metrics-table.py}
        \caption{Image metrics for the difference source scenarios and methods.}
    \end{table}

@@

    We compute the full-width at half-max (FWHM), $\omega$, of the profiles for each bootstrapped data set, by fitting a Gaussian shape with a linear gradient as a baseline for both the original counts and the \jolideconospace-deconvolved intensities. In both cases we compute the mean of $\omega$. We find that the deconvolved profile is significantly narrower. For the counts profile, $\omega_C=0.78 \pm 0.02$~arcsec, where the error bar is obtained by computing the standard deviations of $\omega$ over the bootstrap sample; and the deconvolved intensity profile has $\omega_J=0.58 \pm 0.02$~arcsec.
